---
title: "Homework 01"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this assignment we are supposed to do some explorations on a dataset.

## Set up the environment

The dataset I choose to use is gapminder. Notice that gapminder is not installed defaultly, so before any exploration first you need to get it installed like this:

```{r results='hide'}
install.packages("gapminder")
```

Then the package should be loaded before we use it, like import things in python:

```{r}
library(gapminder)
```

Now we are ready to go.

## Basic informations of the dataset

You can just print the dataset like this:

```{r results='hide'}
print(gapminder)
```

But it is presented in a poor way. Luckily there is summary function for showing basic infos of the dataset.

```{r cars}
summary(gapminder)
```

Also there are other handy functions:
```{r}
head(gapminder)
str(gapminder)
ncol(gapminder)
nrow(gapminder)
```

## Further exploration

You can always take a colunm of the dataset for further calculations.
```{r}
head(gapminder$pop)
```

The variance and mean can be easily calculated by using var and mean function.
```{r}
var(gapminder$pop)
mean(gapminder$pop)
```